Meanwhile, neutrinos deposit energy in matter during the interaction, where the amount of energy deposited depends on the flavor of neutrinos. The significance of matter effect on neutrino flavor oscillations has been demonstrated in Mikheyev-Smirnov-Wolfenstein (MSW) effect~\cite{Mikheev:1986gs,wolf78,wolfensteinprd1979}, which is used to explain the deficit of electron flavor neutrino flux, thus solved the solar neutrino problem~\cite{Petcov2002,kuo1989}. Later developments on the theories about matter effect revealed the parametric resonance of neutrino flavor oscillations due to fluctuations in matter density~\cite{Krastev1989,Akhmedov2000}, which is the neutrino analog of transitions between energy levels as a result of external optical stimulation. Parametric resonance is different from the MSW effect since it involves the parameters of the matter density, which is usually the period of matter density fluctuations. Neutrinos passing through inside the Earth can experience parametric resonance~\cite{Akhmedov1999, Petcov1998b}.

As one of the most intense neutrino sources, supernova neutrinos experience turbulent matter density as they propagate through out the explosion~\cite{Muller2015, Couch2015}, where the flavor conversion is modified by interaction with matter. Meanwhile with neutrinos depositing energy into the shock, neutrino flavor conversion is crucial to the shock evolution of supernova explosion. The turbulent matter density environment for neutrino flavor conversion has been researched~\cite{Loreti1994, Friedland2006,Kneller2010}. Recently matter stimulated neutrino flavor conversion in varying matter density has been researched using Jacobi-Anger expansion by Kneller, et al.~\cite{Kneller2013,Patton2014}. They have shown that many stimulated neutrino flavor conversions can be explained by resonances of the system.

We will take a step further and interpret parametric resonance~\cite{Akhmedov2000, Krastev1989} as well as other matter stimulated neutrino flavor conversions~\cite{Kneller2013, Patton2014}, as superposition of Rabi oscillations. We also propose a criteria for the interference effect between different Rabi oscillation modes. In Sec.~\ref{chap:matter-sec:background}, we define the formalism of neutrino flavor conversions in matter used in this chapter where the equation of motion and Hamiltonian for neutrino flavor conversion in matter are explicitly written. In Sec.~\ref{chap:matter-sec:single} we discuss how neutrino flavor conversions are related to Rabi oscillations. To begin with, we discuss a system with single frequency matter density fluctuation. We will show that such a system can be reduced to Rabi oscillations if resonance occurs. In Sec.~\ref{chap:matter-sec:multiple-matter-frequencies} we describe the interference effect between different frequencies of Rabi oscillations and develop the criteria for significant interference between two frequencies. We show that the interference between the many frequencies fits into the criteria we proposed for interference. In Sec.~\ref{sec:jacobi} we discuss the technique of decomposing the neutrino flavor conversions into summation of Rabi oscillations, by applying a specific unitary transformation and the Jacobi-Anger expansion. As the system is exactly decomposed into multiple Rabi oscillations, we can interpret neutrino flavor oscillations in any matter density fluctuations in principle. As an example, we solve the neutrino flavor transitions in a castle wall matter profile, which is expanded using Fourier series into many frequencies.
